Model LF

### 2022-11-29 max_dp endogen stød.Rmd
Commit

```{r}
plot((unemp_000-unemp_bs1)*1000, col= "red")
```

@@

```{r}
plot(wage_ds_02, col= "red"); lines(wage_ds_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

>>>>

```{r}
plot((emp_000-emp_bs1)*1000, col= "red");
lines((emp_01-emp_00)*1000)
```

@@

```{r}
plot(wage_ds_02, col= "red"); lines(wage_ds_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(((xk_ds_02 - xk_ds_bs2)), col= "black", xlab= "Year", ylab= "Change in GDP", main= "GDP");
grid()
```
